Interest Flooding Attacks and Countermeasures in Named Data Networking

### 2013-01-14 04-design.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@919 df1a90cd-247b-4364-bdaf-287a704eb499

In this section we present several algorithms to mitigate Interest flooding attacks in NDN.  Our mitigation strategies feature varying degrees of implementation complexity and effectiveness---the higher the implementation complexity, the more effective is the algorithm against Interest flooding attacks. We start by describing our simple strategies and use the insights and lessons learnt from the deployment of these techniques to inform and design more effective mitigation techniques that can work well in a variety of attack scenarios.

@@

In order to distinguish between legitimate and malicious Interests, we leverage another unique feature of  NDN architecture---guaranteed symmetric flow of Interest and Data packets. Since a Data packet takes the reverse path of the corresponding Interest packet, a router is guarateed to see if an Interest it forwarded resulted in a matching Data packet. The only exception being if Interest/Data packets were lost along the way due to congestion in the network.
Therefore, intermediate routers can classify all Interests that result in matching Data as legitimate, while the ones that timed out can be marked as malicious.\footnote{Recall that in order to maximize effect of the Interest flooding attack, an adversary expresses a large volume of junk Interests (see Section~\ref{sec:interest-flooding}).}  
%Implications of other types of attacks are discussed in Section~\ref{sec:discussion}.}

This timeout-based differentiation method is reactive in nature: one cannot determine in advance if an Interest will result in a timeout or Data being retrieved. However, routers can proactively maintain up-to-date statistics of Interest satisfaction ratios (number of forwarded versus number of satisfied Interests), and use this statistic to determine whether an incoming Interest must be forwarded or dropped. For example, maintaining independent Interest satisfaction ratio statistics for each incoming interface is sufficient to estimate whether an Interest received from a neighbor connected to this interface will result in a Data packet or a timeout. Statistics can also be kept at finer granularities such as per outgoing interface, per name prefix, etc. that can further improve the estimates. A router's goal should be to penalize malicious Interests as soon as possible---negative statistics should be allowed to build up fast, while positive statistics should not be allowed to deteriorate too quickly. We use the standard exponentially weighted moving average, performed once a second with $\alpha$ coefficient $e^{-1/30}$, approximately corresponding to a 30-second averaging window to achieve the above goal.

>>>>

In this section we present several algorithms to mitigate Interest flooding attacks in NDN.  Our mitigation strategies feature varying degrees of implementation complexity and effectiveness---the higher the implementation complexity, the more effective is the algorithm against Interest flooding attacks. We start by describing our simple strategies and use the insights and lessons learned from the deployment of these techniques to inform and design more effective mitigation techniques that can work well in a variety of attack scenarios.

@@

In order to distinguish between legitimate and malicious Interests, we leverage another unique feature of  NDN architecture---guaranteed symmetric flow of Interest and Data packets. Since a Data packet takes the reverse path of the corresponding Interest packet, a router is guaranteed to see if an Interest it forwarded resulted in a matching Data packet or times out. %The only exception being if Interest/Data packets were lost along the way due to congestion in the network.
Since malicious Interests are not likely to bring data back (as discussed in Section~\ref{sec:interest-flooding}), this information can be utilized by routers in differentiating attack and legitimate traffic.  %Therefore, intermediate routers can classify the ones that brings data back as legitimate, while the ones that timed out can be marked as malicious.\footnote{Recall that in order to maximize effect of the Interest flooding attack, an adversary expresses a large volume of junk Interests (see Section~\ref{sec:interest-flooding}).}  
%Implications of other types of attacks are discussed in Section~\ref{sec:discussion}.}

This timeout-based differentiation method is reactive in nature: one cannot determine in advance if an Interest will result in a timeout or Data being retrieved. However, routers can proactively maintain up-to-date statistics of Interest satisfaction ratios (number of forwarded versus number of satisfied Interests), and use this statistic to determine whether an incoming Interest should be forwarded or dropped. For example, maintaining independent Interest satisfaction ratio statistics for each incoming interface is sufficient to estimate whether an Interest received from a neighbor connected to this interface will result in a Data packet or a timeout. Statistics can also be kept at finer granularities such as per outgoing interface, per name prefix, etc. that can further improve the estimates. A router's goal should be to prioritize Interests that bring Data back while quickly penalizing those that occupy resources but don't generate a Data stream in return. In order to allow negative statistics to build up fast and positive statistics deteriorate quickly, we use the standard exponentially weighted moving average, performed once a second with $\alpha$ coefficient $e^{-1/30}$, approximately corresponding to a 30-second averaging window.

### 2013-01-14 05-evaluation.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@919 df1a90cd-247b-4364-bdaf-287a704eb499

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "paper"
%%% End:

>>>>

\subsection{Limitations}
{\color{red} I gave up the idea of seperate discussion section as after trying for some time, I realized there is no way to write a reasonably comprehensive and acceptably broad discussion section that touches on algorithms, evaluation and methodology, etc. So, I decided to get rid of it and only have a scoped down version here that confesses upon the limiations of our evaluations. Whoever has time, please go ahead and write 1-2 paragraphs as outlined below}

This section should roughly say: Our results show that the two features, namely the symmetric traffic and stateful routing, give NDN routers the ability to observe and characterize traffic in real time. Through our evaluations, we demonstrated that a mitigation algorithm that leverages such ability has great potential in mitigating various DDoS attacks that could otherwise have grave effect on the network. However, as the first step in exploring the problem and the solution space, this paper has obvious limitations: (1) We assume a simple attacker model that would be most effective in vanilla NDN and keep it static during our evaluations. Although it is a valid and important step in showing the effectiveness of a particular mitigation approach, the next natural step is evaluating the above described solutions with more sophisticated and adaptive attackers. (2)   Although most (such as single-path routing, no-caches in the network, single homed victim, etc) are aimed to test the proposed solutions under worst-case scenario, we made many assumptions in simulations/evaluations about the configurations, topology and the traffic that maybe poor-representative of realistic conditions. (3) As NDN being an ongoing research effort itself, our evaluations fully depend on simulations and done over a snapshot of its codebase.

### 2013-01-14 paper.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@918 df1a90cd-247b-4364-bdaf-287a704eb499
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@919 df1a90cd-247b-4364-bdaf-287a704eb499

\title{Interest Flooding Attacks and countermeasures in Named Data Networking}%:\\ Cache/Content Poisoning}
%\author{Anonymous}

@@

\input{04a-design-naive}

\input{04b-design-intelligent}

@@

\input{07-discussion}

@@

\bibliographystyle{IEEEtran}
{\small 
\bibliography{references}
}

>>>>

\title{Interest Flooding Attacks and Countermeasures in Named Data Networking}%:\\ Cache/Content Poisoning}

%I don't think submission is anonymous...
% I PUT AUTHOR NAMES IN ALPHEBETICAL ORDER. It is the common practice in security and I always list authors alphebetically in my publications. -Ersin 
\author{
    \IEEEauthorblockN{Alexander Afanasyev\IEEEauthorrefmark{1}, Priya Mahadevan\IEEEauthorrefmark{2}, Ilya Moiseenko\IEEEauthorrefmark{1}, Ersin Uzun\IEEEauthorrefmark{2}, Lixia Zhang\IEEEauthorrefmark{1}}
    \IEEEauthorblockA{\IEEEauthorrefmark{1}University of California, Los Angeles
    \\\{alex, ilya, lixia\}@ucla.edu}
    \IEEEauthorblockA{\IEEEauthorrefmark{2}Palo Alto Research Center
    \\\{ersin.uzun, priya.mahadevan\}@parc.com}
}

@@

\input{04-design}

@@

@@

\bibliographystyle{IEEEtran}
\bibliography{references}
